---
title: "Keller_Reveiw"
author: "Alex Keller"
date: "2023-03-16"
output: html_document
---
I think you did very well. Just a few things that did not want to run for me that are commented below.
Great work!

Ahmed's comment on your review: I attached another R markdown file that have updated commands that won't stuck at all as well as an HTML ouput file.


First is that there is not Rmarkdown file, just a README.md/ 
Second, I was unable to run the whole script all at once. It got stuck on the the code below with the following error:
Error: Incomplete expression: write.csv(headsoff_transposed_maize_fang, "headsoff_transposed_maize_fang.csv", row.nam
```{r}
write.csv(headsoff_transposed_maize_fang, "headsoff_transposed_maize_fang.csv", row.nam
```

The fix here is just finishing the line of code.
```{r}
write.csv(headsoff_transposed_maize_fang, "headsoff_transposed_maize_fang.csv", row.names = FALSE)
```


Make sure that you have the code for all 10 seperate chromosomes writen so that it can be ran all at once and have all the chromsome files made.

Due to what I have mentioned above, I am unable to run this code because you don't have this file being made in the code as it is currently.
Error message I got:
  Warning: cannot open file 'down_maize2_snp.csv': No such file or directoryError in file(file, "rt") : cannot open the connection
  Error in is.data.frame(x) : object 'down_maize2_snp' not found

```{r}
down_maize1_snp <- read.csv("down_maize2_snp.csv")

write.csv(down_maize2_snp, "edited-down_maize1_snps.csv", row.names = FALSE)
```

As mentioned in class you should not include install.packages()

I got this error message for this chunk of code, I'm not sure what it means though...
Error: no loop for break/next, jumping to top level

```{r}
ggplot(sample_summary_data, aes(x = Sample_ID)) +
    geom_bar(aes(y = prop_homozygous, fill = "Homozygous"), alpha = 0.8, stat = "identity") +
    geom_bar(aes(y = prop_heterozygous, fill = "Heterozygous"), alpha = 0.8, stat = "identity") +
    geom_bar(aes(y = prop_missing, fill = "Missing"), alpha = 0.8, stat = "identity") +
    scale_fill_manual(values = c("Homozygous" = "darkgreen", "Heterozygous" = "yellow", "Missing" = "gray")) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    labs(x = "Sample ID", y = "Proportion", fill = "Site Type", 
         title = "Proportion of Homozygous, Heterozygous, and Missing Sites by Sample ID")
```


